Wi-Fi Based Handwritten Signature Verification Using a Triplet Network

### 2019-09-07 190906_Paper_BDML/bdml_v0.tex
Conf_BDML

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}

\begin{document}
%
\title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
%
\titlerunning{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
To enable a fast loss convergence, a kernel and the range space learning is initially adopted for refining the triplet inputs by mining the distinctive inputs. 
Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

\keywords{Wi-Fi signature signal \and in-air handwritten signature verification \and the Kernel and the Range space projection learning \and triplet network}
\end{abstract}
%
%
%
\section{Introduction}

Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}. Among these behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or a mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems.

@@

% Karnet structure and mining samples.
Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
Then the multilayer neural network structure can be written in linear equation form as follows:
\begin{equation}
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), i=1,\dotsc,n,
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:

\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), i=1,\dotsc,n.
\end{equation}

@@

% Figure 1
\begin{figure}[!ht]
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v5}
    \caption{An overview of the proposed system.} \label{fig1}
\end{figure}

@@

By training the network with the single shot KAR space learning, we can map the L-2 distance between every samples by using the output vector of the KAR space network. \textbf{For training dataset $\mathbf{X}$, the trained network output is given by:}
\begin{equation}
    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
\textbf{For anchor sample $\mathbf{x}_{anc}$ which is randomly selected from training dataset X, the output of the KAR learning makes it possible to measure the distance between each sample.}
A hard positive sample $\mathbf{x}_{pos}$ and a hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can each be respectively determined based on:
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
\end{equation}
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
\end{equation}
where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ respectively denote the thresholds that determine whether a sample is hard positive or hard negative. Since the hardest samples are likely to be outliers which can degrade the training process of the triplet network, we empirically set the $\mathrm{t}_{pos}$ at 75 percentile of the L-2 distance and $\mathrm{t}_{neg}$ at 25 percentile of the L-2 distance. The final set of $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ samples is randomly selected from those samples threshold by~\eqref{pos} and~\eqref{neg}.

@@

The next step is to design a feature extractor which converts the input triplet data into feature vectors. In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three-dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.

@@

The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
\textbf{For selected anchor input sample $\mathbf{x}_{anc,i}$, the $i_{th}$ triplet input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$ is generated by grouping positive input sample $\mathbf{x}_{pos,i}$ and the negative input sample $\mathbf{x}_{neg,i}$.
The generated triplet input is fed into ConvNet structure and make feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$.}
The triplet loss function is formulated based on a summation of the difference between the positive distance (the L-2 distance between the anchor vector and the positive vector) and the negative distance (the L-2 distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
\end{equation}
where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\subsubsection{Performance evaluation:}
The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve. For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.

\begin{table}[]
    \caption{The network structure of KAR space learning.}\label{tab2}
    \centering
    \begin{tabular}{|l|l|l|}
    \hline
    Layer   & Size     & Activation \\ \hline
    Input   & 500$\times$30$\times$6 &            \\
    Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
    Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
    Output  & 1$\times$1$\times$50   &            \\ \hline
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for the output layer. The output layer was regularized using an L-2 penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation of 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE,SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
 \begin{table}[]
    \caption{
        The structure of ConvNet model. For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride. For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters. 
    }\label{tab1}
    \centering
    \begin{tabular}{|c|c|c|c|}
    \hline
    Layer     & Activation & Kernel / Stride & Input Size \\ \hline
    Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
    MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
    Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
    MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
    Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
    MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
    Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
    L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
    Concat    &            &                 & 1$\times$1$\times$16    \\ \hline
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition. Among the handcraft methods, the SVM with RBF kernel showed the best verification accuracy of 24.31\% EER followed by the SVM with Linear kernel function. However, all three deep learning-based methods showed better performance than the SVM with RBF kernel function since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.
Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
The best average of test EER performance was obtained from the proposed system with 19.35\% EER. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER.
\begin{table}[!h]
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset.}\label{tab3}
    \centering
    \begin{tabular}{|c|c|c|}
    \hline
    Methology   &   Best EER (\%) &   Condition   \\  \hline
    LSE &   48.44   &  - \\ 
    PCA-LSE    &   30.79   &  Reduced dimension=40    \\
    SVM (Linear) &   28.23   &   c=1 \\
    SVM (RBF)    &   24.31   &   c=1, $\gamma$=0.01/3000 \\
    TER-RM2 &   35.84   &  M=1,$\tau$=$\eta$=0.5   \\     \hline
    Siamese network  &   23.53   &   lr=0.00005  \\
    Baseline triplet network &   20.34   &   lr=0.00005, $\alpha$=0.1  \\
    \textbf{Proposed system} &   \textbf{19.35}   &  \textbf{lr=0.00005, $\alpha$=0.1}  \\
     \hline
    \end{tabular}
\end{table}
Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods. As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods while other two methods show similar AUC. Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value based on their function. According to these two observations, it can be concluded that the triplet input mining with KAR space learning improves not only the training loss convergence speed but also the verification performance.

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}
\usepackage{multirow}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{rightsretained}

%% These commands are for a PROCEEDINGS abstract or paper.
%\acmConference{SIGGRAPH '19 Talks}{July 28 - August 01, 2019}{Los Angeles, CA, USA}
%\acmDOI{10.1145/3306307.3328180}
%\acmISBN{978-1-4503-6317-4/19/07}
%\acmBooktitle{SIGGRAPH '19 Talks, 
%  July 28 - August 01, 2019, Los Angeles, CA}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Wi-Fi Based Handwritten Signature Verification Using a Triplet Network}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Young-Woong Kwon}
%\authornote{Both authors contributed equally to this research.}
\email{herokwon@yonsei.ac.kr}
\affiliation{%
  \institution{School of Electrical and Electronic Engineering, Yonsei University}
  \streetaddress{50 Yonsei-ro}
  \city{Seodaemun-gu}
  \state{Seoul}
  \postcode{03722}
}

\author{Jooyoung Kim}
%\authornote{Both authors contributed equally to this research.}
\email{harrykim@yonsei.ac.kr}
\affiliation{%
  \institution{School of Electrical and Electronic Engineering, Yonsei University}
  \streetaddress{50 Yonsei-ro}
  \city{Seodaemun-gu}
  \state{Seoul}
  \postcode{03722}
}

\author{Kar-Ann Toh}
%\authornote{Both authors contributed equally to this research.}
\email{katoh@yonsei.ac.kr}
\affiliation{%
  \institution{School of Electrical and Electronic Engineering, Yonsei University}
  \streetaddress{50 Yonsei-ro}
  \city{Seodaemun-gu}
  \state{Seoul}
  \postcode{03722}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Y.Kwon, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi Channel State Information (CSI). 
    To enable a fast loss convergence, a kernel and the range space learning is initially adopted for refining the triplet inputs by mining the distinctive inputs. 
    Subsequently, the triplet network is trained on a ConvNet structure using the mined triplet inputs. 
    Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

\begin{CCSXML}
    <ccs2012>
    <concept>
    <concept_id>10002978.10002991.10002992.10003479</concept_id>
    <concept_desc>Security and privacy~Biometrics</concept_desc>
    <concept_significance>500</concept_significance>
    </concept>
    <concept>   
    <concept_id>10010147.10010257.10010293.10010294</concept_id>
    <concept_desc>Computing methodologies~Neural networks</concept_desc>
    <concept_significance>500</concept_significance>
    </concept>
    </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Biometrics}
\ccsdesc[500]{Computing methodologies~Neural networks}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Wi-Fi signature signal, in-air handwritten signature verification, the Kernel and the Range space projection learning, triplet network}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%\begin{teaserfigure}
%  \includegraphics[width=\textwidth]{sampleteaser}
%  \caption{Seattle Mariners at Spring Training, 2010.}
%  \Description{Enjoying the baseball game from the third-base
%  seats. Ichiro Suzuki preparing to bat.}
%  \label{fig:teaser}
%\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

%Intro
\section{Introduction}
Over recent years, several behavioral biometric traits attracted attention in view of their rigid physical body independence~\cite{bailador2011analysis}. Among these behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} has attracted considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or a mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower the spatial constraint in the process of signature acquisition comparing with contact-based authentication systems.

@@

% Karnet structure and mining samples.
Given $m$ training samples. Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
Then the multilayer neural network structure can be written in linear equation form as follows:
\begin{equation}
\begin{split}    
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),\\ i=1,\dotsc,n,
\end{split}
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,\\$\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is the activation function.
By adopting an one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$, training of the weight matrices $\mathbf{W}_{i}$ using the KAR space method~\cite{toh2018gradient} can be computed as follows:
\begin{equation}
\begin{split}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), \\ i=1,\dotsc,n.
\end{split}
\end{equation}

@@

% Figure 1
\begin{figure*}[!ht]
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v6}
    \caption{An overview of the proposed system} \label{fig1}
\end{figure*}

@@

By training the network with the single shot KAR space learning, we can map the L-2 distance between every samples by using the output vector of the KAR space network. \textbf{For training data set $\mathbf{X}$, the trained network output is given by:}
\begin{equation}
    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
\textbf{For anchor sample $\mathbf{x}_{anc}$ which is randomly selected from training dataset X, the output of the KAR learning makes it possible to measure the distance between each sample.}
A hard positive sample $\mathbf{x}_{pos}$ and a hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can each be respectively determined based on:
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
\end{equation}
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
\end{equation}
where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ respectively denote the thresholds that determine whether a sample is hard positive or hard negative. Since the hardest samples are likely to be outliers which can degrade the training process of the triplet network, we empirically set the $\mathrm{t}_{pos}$ at 75 percentile of the L-2 distance and $\mathrm{t}_{neg}$ at 25 percentile of the L-2 distance. The final set of $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ samples is randomly selected from those samples threshold by~\eqref{pos} and~\eqref{neg}.

@@

The next step is to design a feature extractor which converts the input triplet data into feature vectors. In this work, we utilize the ConvNet structure~\cite{lecun1998gradient} as a feature extractor since the three dimensional data format of our preprocessed input signal can be regarded as an image data format with multiple channels.

@@

The triplet loss function was first seen in \cite{hoffer2015deep} for training the triplet network.
\textbf{For the $i^{th}$ network input $\left\{\mathbf{x}_{anc,i}, \mathbf{x}_{pos,i}, \mathbf{x}_{neg,i}\right\}$, anchor sample $\mathbf{x}_{anc,i}$ is randomly selected among the training data set. Positive sample $\mathbf{x}_{pos,i}$ is selected among the same class with the anchor while negative sample $\mathbf{x}_{neg,i}$ is selected among the different class with the anchor. The generated triplet input is fed into ConvNet structure and make feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$.}
The triplet loss function is formulated based on a summation of the difference between the positive distance (the L-2 distance between the anchor vector and the positive vector) and the negative distance (the L-2 distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]},0 \right),\label{triplet}
\end{equation}
where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\subsubsection{Performance evaluation:}
The proposed system is evaluated under two cases: i) case I on comparison between the proposed system and other handcraft or deep learning-based methods based on the verification accuracy, and case II on detailed comparison between the proposed system and the deep learning-based methods using the receiver operating characteristic (ROC) curve and training loss curve. \textbf{We considered in-air signature data could be entered in any direction of the Wi-Fi router. For 4-way inputs, we take into account with signatures facing Wi-Fi router's front, rear and both sides. For 1-way inputs, we considered only the entered signatures facing the forward face of the Wi-Fi router.} For Case I, existing handcraft methods such as the least squares error estimation (LSE), the principal components analysis (PCA) [22] with LSE, the support vector machine (SVM) with different kernel functions and a total error rate minimization which adopted the reduced multivariate polynomial model as basis function (TER-RM2) \cite{toh2003fingerprint,toh2008between}, the deep learning-based Siamese network \cite{koch2015siamese} and the baseline triplet network \cite{hoffer2015deep} are included for performance benchmarking. The Siamese network and the baseline triplet network utilized the same ConvNet structures with the proposed system and only differed in their input data style and loss function.

@@

\subsubsection{Network Structure and Parameter Settings:}
The multilayer feedforward network structure of KAR space learning is specified in Table~\ref{tab2}. With input data, size of 500$\times$30$\times$6, we set two network layers where the size of the each layer is 1024 and 16, respectively. Each layer is initialized with uniform distribution over [0, 1). We used $\sigma = {tan}^{-1}$ as an activation function following \cite{toh2018analytic}.
\begin{table}
    \caption{The network structure of KAR space learning}
    \label{tab2}
    \begin{tabular}{ccc}
     \toprule
     Layer   & Size     & Activation \\
     \midrule
     Input   & 500$\times$30$\times$6 &            \\
     Fully-Connected 1 & 1$\times$1$\times$1024 & $\sigma = {tan}^{-1}$     \\
     Fully-Connected 2 & 1$\times$1$\times$16  & $\sigma = {tan}^{-1}$     \\
     Output  & 1$\times$1$\times$50   &            \\
     \bottomrule
    \end{tabular}
\end{table}

For the proposed system and the deep learning-based methods, we utilized the same ConvNet structure as specified in Table~\ref{tab1}. We trained the network starting with a learning rate of 0.00005 and a mini-batch size of 32. We optimized the loss by the Adam optimizer with L-2 penalty of 0.0002 except for the output layer. The output layer was regularized using an L-2 penalty of 0.0001. We initialized all network weights in the convolutional layers with normal distribution of zero-mean and standard deviation 0.01. The biases were also initialized with a normal distribution of 0.5 mean and standard deviation 0.01. For the triplet networks, the hyper-parameter regulating triplet loss is empirically set at 0.1. The training epochs were set at 1,500 for all three deep learning-based algorithms. For the linear methods such as LSE,SVM and TER, the input signals were resized to 500 $\times$ 30 by averaging along the subcarrier axes due to limitation of hardware memory. For the PCA-LSE, the input dimension was reduced to 40.
\begin{table}
    \caption{The structure of ConvNet model. For the convolution layer, kernel is specified as (m$\times$m) sized filter $\times$ \# of filters / \# of stride. For the max-pooling layer, (p$\times$p) sized pooling windows / \# of stride. The input sizes are denoted as rows $\times$ cols $\times$ \# of filters}
    \label{tab1}
    \begin{tabular}{cccc}
     \toprule
     Layer     & Activation & Kernel / Stride & Input Size \\
     \midrule
     Conv 1    & ReLU       & (3$\times$3)$\times$64/1      & 500$\times$30$\times$6   \\
     MaxPool 1 &            & (2$\times$2)/1         & 500$\times$30$\times$64  \\
     Conv 2    & ReLU       & (3$\times$3)$\times$128/1     & 250$\times$15$\times$64 \\
     MaxPool 2 &            & (2$\times$2)/1         & 250$\times$15$\times$128 \\
     Conv 3    & ReLU       & (3$\times$3)$\times$256/1     & 125$\times$8$\times$128  \\
     MaxPool 3 &            & (2$\times$2)/1         & 125$\times$8$\times$256  \\
     Fully-Connected     & Sigmoid    & 16             & 63$\times$4$\times$256   \\
     L-2 Norm  &            &                 & 1$\times$1$\times$16    \\
     Concat    &            &                 & 1$\times$1$\times$16    \\
     \bottomrule
    \end{tabular}
\end{table}

@@

Case I: Table~\ref{tab3} shows the best average of EER performance from five runs of two-fold cross-validation test and the parameter condition. 
\textbf{For 1-way inputs, SVM showed best verification accuracy of 1.55\% EER. However, For 4-way inputs, all three deep learning-based methods showed better performance since the deep learning-based methods could utilize the original size (500$\times$30$\times$6) of the input data in the training stage.} Among the deep learning-based methods, the Siamese network is also a metric learning system, but it differs from our system in that it receives two inputs and uses the contrastive loss function for training. 
The best average of test EER performance was obtained from the proposed system with 19.35\% EER. The baseline triplet network without input mining showed slightly worse performance of 20.34\% EER. The Siamese network showed the worst verification performance of 23.53\% EER.
\begin{table}
    \caption{Performance benchmarking with respect to the best EER (\%) averaged from five runs of two-fold cross-validation test on Wi-Fi CSI signature dataset}
    \label{tab3}
    \begin{tabular}{cccl}
    \toprule
    \multirow{2}{*}{Methology} & \multicolumn{2}{c}{Best EER (\%)} & \multirow{2}{*}{Condition} \\ \cline{2-3}
                            & 1-way     & 4-way     &                            \\
    \midrule
    LSE                                    & 35.40 & 48.44           &                           \\ 
    PCA-LSE                                & 16.87 & 30.79           & $d_{3000} \rightarrow d_{40}$       \\ 
    SVM(Linear)                            & 1.55 & 28.23            & c=1                        \\ 
    SVM(RBF)                               & 3.97 & 24.31            & c=1, $\gamma$=0.01/3000    \\ 
    TER-RM2                                & 13.29 & 35.84          & M=1,$\tau$=$\eta$=0.5      \\
    \midrule
    Siamese network                        & 16.86 & 23.53           & lr=0.00005                 \\ 
    Baseline triplet network               & 5.45 & 20.34           & lr=0.00005, $\alpha$=0.1   \\ 
    \textbf{Proposed system}               & \textbf{5.09} & \textbf{19.35}           & \textbf{lr=0.00005, $\alpha$=0.1}   \\
    \bottomrule
    \end{tabular}
\end{table}

Case II: Fig.~\ref{fig2}(a) shows the ROC curve of three deep learning-based methods. As shown in the Fig.~\ref{fig2}(b), the proposed system clearly shows the largest Area Under Curve (AUC) among three compared methods while other two methods show similar AUC. Moreover in Fig.\ref{fig2}(b) which illustrates the training loss curve along the number of training iteration, the proposed system shows the fastest training loss convergence followed by the baseline triplet network. We note here that the y-axes of triplet network based methods and the Siamese network are normalized into $[0,1]$ since each loss function has different starting value based on their function. According to these two observations, it can be concluded that the triplet input mining with KAR space learning improves not only the training loss convergence speed but also the verification performance.
% Figure 2,3
\begin{figure}[!ht]
    \begin{center}
    \subfigure[][ROC Curve]{
        \includegraphics[height=6.4cm]{fig_roc_v12.eps}}
    \subfigure[][Normalized training loss curve]{
        \includegraphics[height=6.4cm]{normalized_loss_curve_ma30_v2.eps}}
    \caption{(a) shows the Receiver Operating Characteristic(ROC) Curve and 
    (b) shows the normalized training loss curve of the deep learning based methods}
    \label{fig2}
    \end{center}
 \end{figure}
